\gettitle

### 2019-11-15 assignment2/submission2.tex
Exercise 1 solution added

\section*{1 - Parameter Passing and RMI}
\subsection*{a)}
\begin{enumerate}[label=(\roman*)]
	\item 
	\item 
	\item 
\end{enumerate}

\subsection*{b)}

>>>>

\section*{1 - Parameter Passing and RMI}
\subsection*{a)}
\begin{enumerate}[label=(\roman*)]
	\item [1, 2, 3, 4, 5]
	\item [5, 4, 2, 4, 5]
	\item [1, 2, 3, 4, 5] or [5, 4, 3, 2, 1] depending on the order in which the arrays are copied back.
\end{enumerate}

\subsection*{b)}
All objects that extend UnicastRemoteObject are send as reference, all other objects are send as value.
In the frist and last two lines the parameter is a StringBuffer object wich does not implement UnicastRemoteObject and send as value. In the third line the parameter is a StringServer object wich does implement UnicastRemoteObject and because of this is send as reference.
\subsection*{c)}
Call-by-Value has a huge overhead if a large structure is given of wich only a small part is writen/read.
Call-by-reference has a huge overhead if it is often writen/read.
